Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-08 paper.qmd
Updated Figure 11

## Compute hexbin parameters
num_bins_x_gau1 <- 35
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 127
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 56
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

>>>>

## Compute hexbin parameters
num_bins_x_gau1 <- 26
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 90
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 40
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)
